
---
title: "Marketing Campaign Analysis"
author: "Krrish Jambhulkar"
format: 
  html: default
  pdf: default
execute:
  echo: false
  warning: false
  message: false
editor: visual
---




```{r}
#| label: setup
#| include: false

library(tidyverse)
library(knitr)

# Load your unique data
marketing_data <- read_csv("data/36709859_Krrish Jambhulkar.csv")
```

## Introduction

As the Head of Marketing, I reviewed the recent campaign to assess its impact on customer purchasing behaviour. This analysis was conducted to ensure our budget is being allocated effectively across different business segments. We evaluated the relationship between marketing spend and customer purchases to identify the most profitable strategies. These insights will guide our future campaigns by focusing on the customer behaviours that drive the best results.



## Research Question

Did increased marketing spend encourage customers to make more purchases? We will analyze the patterns to determine which segments responded best to our campaign. Based on these insights, we can make informed decisions about allocating our future marketing budget.

## Dataset Introduction
This dataset contains information on 150 customers from a marketing campaign conducted last quarter. For each customer, we have tracked their total spending and the number of visits, along with the marketing spend allocated per customer. Customers are also categorised into three segments: Consumer, SMB, and Enterprise.

Before analysis, data cleaning was performed to ensure consistency and accuracy. Date values were in multiple formats, so they were standardised into a single format. Customers who neither visited nor made any purchases were removed, as they did not contribute to the analysis, and the notes column was dropped due to its lack of relevant information.
```{r}
#| label: data-cleaning
#| include: false

marketing_data <- read_csv("data/36709859_Krrish Jambhulkar.csv") %>%
  mutate(
    signup_date = parse_date_time(signup_date, 
                  orders = c("ymd", "dmy", "mdy", "B d, Y")) %>% 
                  as.Date()
  ) |>
  filter(!is.na(purchase_amount), purchase_amount > 0) %>%
  filter(visits > 0) %>%
  select(-notes)
```

### Dataset Description

After cleaning, the dataset contains `r nrow(marketing_data)` observations 
and `r ncol(marketing_data)` variables. The variables include customer ID, 
signup date, marketing spend, visits, purchase amount, and segment, which 
are a mix of numeric and categorical variables.
```{r}
#| label: tbl-segment-summary
#| echo: false
#| tbl-cap: "Average marketing spend and purchase amount by segment"

marketing_data %>%
  group_by(segment) %>%
  summarise(
    Mean_Marketing_Spend = round(mean(marketing_spend), 2),
    Mean_Purchase_Amount = round(mean(purchase_amount), 2)
  ) %>%
  kable()
```
```{r}
#| label: fig-segment-count
#| echo: false
#| fig-cap: "Number of customers per segment"

ggplot(marketing_data, aes(x = segment)) +
  geom_bar(fill = "steelblue") +
  labs(x = "Segment", y = "Number of Customers") +
  theme_minimal()
```

## Results

## Results

@fig-spend-purchase illustrates the relationship between marketing 
spend and purchase amount across all customers. The upward trend from 
left to right indicates that higher marketing spend is associated with 
increased purchase amounts. @fig-spend-segment presents the same 
relationship segmented by customer groups. All three segments Consumer, 
SMB and Enterprise show a similar upward trend, suggesting that higher 
spend leads to increased purchases across all customer groups.
```{r}
#| label: fig-spend-purchase
#| echo: false
#| fig-cap: "Relationship between marketing spend and purchase amount"

ggplot(marketing_data, aes(x = marketing_spend, y = purchase_amount)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE) +
  labs(x = "Marketing Spend ($)", y = "Purchase Amount ($)") +
  theme_minimal()
```
```{r}
#| label: fig-spend-segment
#| echo: false
#| fig-cap: "Relationship between marketing spend and purchase amount by segment"

ggplot(marketing_data, aes(x = marketing_spend, y = purchase_amount, 
                            color = segment)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE) +
  labs(x = "Marketing Spend ($)", y = "Purchase Amount ($)", 
       color = "Segment") +
  theme_minimal()
```





