
---
title: "Marketing Campaign Analysis"
author: "Krrish Jambhulkar"
format: 
  html: default
  pdf: default
execute:
  echo: false
  warning: false
  message: false
editor: visual
---




```{r}
#| label: setup
#| include: false

library(tidyverse)
library(knitr)

# Load your unique data
marketing_data <- read_csv("data/36709859_Krrish Jambhulkar.csv")
```

## Introduction

As the Head of Marketing, I am evaluating our recent campaign to see if our spending effectively increased customer purchases. This research is motivated by the need to ensure our budget is being used wisely across our different business segments. By looking at the relationship between what we spend and what customers buy, we can identify which strategies are most profitable. This analysis will help us plan future campaigns by focusing on the most successful customer behaviors.



## Research Question

Did spending more on marketing lead to customers buying more? 
We look at whether this pattern holds across different customer 
segments to understand which group responded best to the campaign. 
This will help us decide where to focus our marketing budget in the future.

## Dataset Introduction

This dataset contains information about 150 customers from a 
marketing campaign run last quarter. For each customer, we have 
the amount spent on marketing, how many times they visited, and 
how much they bought. Customers are also grouped into three 
segments Consumer, SMB, and Enterprise.

Before analysing the data, some cleaning was done. Dates were 
written in different formats so they were all converted to the 
same format. Customers who did not make a purchase or had zero 
visits were removed as they are not useful for our analysis. 
The notes column was also removed as it did not have any useful 
information.
```{r}
#| label: data-cleaning
#| include: false

marketing_data <- read_csv("data/36709859_Krrish Jambhulkar.csv") %>%
  mutate(
    signup_date = parse_date_time(signup_date, 
                  orders = c("ymd", "dmy", "mdy", "B d, Y")) %>% 
                  as.Date()
  ) |>
  filter(!is.na(purchase_amount), purchase_amount > 0) %>%
  filter(visits > 0) %>%
  select(-notes)
```

### Dataset Description

After cleaning, the dataset contains `r nrow(marketing_data)` observations 
and `r ncol(marketing_data)` variables. The variables include customer ID, 
signup date, marketing spend, visits, purchase amount, and segment, which 
are a mix of numeric and categorical variables.
```{r}
#| label: tbl-segment-summary
#| echo: false
#| tbl-cap: "Average marketing spend and purchase amount by segment"

marketing_data %>%
  group_by(segment) %>%
  summarise(
    Mean_Marketing_Spend = round(mean(marketing_spend), 2),
    Mean_Purchase_Amount = round(mean(purchase_amount), 2)
  ) %>%
  kable()
```
```{r}
#| label: fig-segment-count
#| echo: false
#| fig-cap: "Number of customers per segment"

ggplot(marketing_data, aes(x = segment)) +
  geom_bar(fill = "steelblue") +
  labs(x = "Segment", y = "Number of Customers") +
  theme_minimal()
```

## Results

@fig-spend-purchase shows the relationship between marketing spend 
and purchase amount across all customers. The trend line goes upward 
from left to right, suggesting that higher marketing spend does lead 
to higher purchase amounts. @fig-spend-segment shows the same 
relationship broken down by segment, where all three segments 
Consumer, SMB and Enterprise show the same upward trend, meaning 
higher spend led to more purchases across all customer groups.
```{r}
#| label: fig-spend-purchase
#| echo: false
#| fig-cap: "Relationship between marketing spend and purchase amount"

ggplot(marketing_data, aes(x = marketing_spend, y = purchase_amount)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE) +
  labs(x = "Marketing Spend ($)", y = "Purchase Amount ($)") +
  theme_minimal()
```
```{r}
#| label: fig-spend-segment
#| echo: false
#| fig-cap: "Relationship between marketing spend and purchase amount by segment"

ggplot(marketing_data, aes(x = marketing_spend, y = purchase_amount, 
                            color = segment)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE) +
  labs(x = "Marketing Spend ($)", y = "Purchase Amount ($)", 
       color = "Segment") +
  theme_minimal()
```





